\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{siunitx}
\usepackage[margin=2cm]{geometry}
\usepackage{cuisine}
\usepackage{microtype}

\begin{document}

\begin{recipe}{Dinner Rolls}{24 Portions}{45 Minutes}
Preheat oven to 400\degrees{} F.

\ingredient[4]{Cups}{Flour}
\ingredient[1]{Packet}{Instant Yeast}
\ingredient[1/3]{Cup}{Sugar}
\ingredient[1]{tsp}{Salt}
\ingredient[1 1/2]{Cups}{Warm Milk}
\ingredient[5]{tbsp}{Melted Butter}
\ingredient[1]{}{Egg}
Combine flour, yeast, sugar, salt, warm milk, butter, and egg in a bowl.
As you mix, incorporate 1/2 cup of flour until ball of dough is formed.
Dough needs to be slightly sticky and soft. Put dough in greased bowl
and cover with towel for 30 minutes at room temperature. Remove towel
and deflate dough lightly. Punch it. Put 2 Ounce balls of dough on
greased pan. Put in oven for 12--15 minutes or until golden brown.
\end{recipe}

\begin{recipe}{Sourdough Biscuits}{}{495 --- 1455 minutes}
Preheat oven to 400\degrees{} F.
\ingredient[8]{tbsp}{Butter}
Chop up cold butter into chunks and add to bowl.
\ingredient[2]{Cups}{Flour}
Add flour to the butter. Cut butter into flour using hands.
\ingredient[1]{Cup}{Sourdough discard}
\ingredient[1]{tbsp}{Sugar}
\ingredient[1/2]{Cup}{Milk}
Add Sourdough discard, sugar, and milk to bowl and mix. Cover with a towl and let rest 8--24 hours.
\ingredient[1]{tsp}{Baking Soda}
\ingredient[2]{tsp}{Baking Powder}
Add baking soda and baking powder. Cut into biscuit shape and cook at 400\degrees{} F for 15--20 minutes.
\end{recipe}

\end{document}